Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2019-09-25 nir_companions.tex
Add a tab to minimise differences.
Accepting some changes

% Abstract of the paper
\begin{abstract}
   {\bl In this paper we attempt to directly detect the near-infrared (nIR) spectrum of candidate brown dwarf (BD) companions around FGK stars to assert or discard their stellar nature. Individual nIR spectra are fitted to a synthetic binary model comprised of two PHOENIX-ACES spectra using a $\chi^2$ approach. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models. This was unable to successfully detect the faint spectra of even the largest companion in the sample. We explore how the companion recovery fitting performs on simulated observations and discuss reasons for the non-detection observed. From the injection-recovery analysis, this technique in its current form, is insufficient to recover a companion below 3800~K which corresponds to an upper mass limit for the companions around \(\rm 600~M_{Jup}\). This work highlights the challenges in the spectral detection of faint companions. We explore the limitations of the companion detection with synthetic models at low companion/host flux ratios below 1 per cent, made difficult by the discrepancy between observed and synthetic spectra around 2100~nm.}

@@

\section{Introduction}
\label{sec:intro}
Brown dwarfs (BDs) are sub-stellar objects unable to achieve hydrogen fusion, with masses around \(13-80~\textrm{M}_{Jup}\)~\citep{chabrier_theory_2000}, bridging the gap between low-mass stars and giant planets. Without sustained fusion, brown-dwarfs cool down over time with an age-dependent cooling rate. Therefore, there is an inherent degeneracy between the mass, age and luminosity of a given BD\citep{burrows_nongray_1997}. This degeneracy may be broken by observation of several parameters, for instance when a BD is in a binary system with a main sequence host star, using both the {\bl host stars' age} and the masses derived from the dynamical motion.

A paucity of BD companions exists in short period orbits around Sun-like stars (\(\lesssim5\)\,AU), compared to stellar or planetary companions, termed the \emph{brown dwarf desert}~\citep{halbwachs_exploring_2000,zucker_analysis_2001,sahlmann_search_2011}. As the number of known BDs orbiting solar type stars is low, the characterization of benchmark BDs in the brown dwarf desert~\citep[e.g.][]{crepp_trends_2016} is beneficial in understanding this sub-stellar population and to help constrain formation and evolution theories~\citep{whitworth_formation_2007}. The BD desert also provides a greater challenge as it reduces the amount of good BD candidates to study.

BDs in binary systems, unlike free-floating BDs, allow for the determination of their masses, when complemented with radial velocity (RV) and astrometry measurements. The RV technique provides the mass lower-limit (\(\textrm{M}_{2}\sin{i}\)) of binary and planetary companions, while complementary astrometry measurements can often provide mass upper-limits~\citep[e.g.][]{sahlmann_search_2011}. Measuring or tightening the constraints of BD masses improves the understanding of mass dependence on BD formation processes. For instance, there is growing evidence that the larger giant planets and BD companions do not follow the well known metallicity-giant planet correlation seen in main-sequence stars with planets~\citep[e.g.][]{santos_spectroscopic_2004,santos_observational_2017, maldonado_searching_2017}. Photometry along with stellar evolution models~\citep[e.g.][]{baraffe_evolutionary_2003,allard_btsettl_2013} can also be used to estimate the mass of BD companions~\citep[e.g.][]{moutou_eccentricity_2017} if there is sufficient orbital separation, and a precise determination of the age~\citep[e.g.][]{soderblom_ages_2010}.

Recently, there has been a renewed interest in BD candidates triggered by exoplanetary searches. While several works found similar properties on the two populations, like a similar {\bl mass} density~\citep{hatzes_definition_2015}, others found intriguing differences. One of the most recent is the different host metallicity of the Brown Dwarf and giant planet populations~\citep{santos_observational_2017, schlaufman_evidence_2018}, a very strong hint of different formation mechanisms.

Spectral observations of binary systems contain the spectra of both bodies, in proportion to their flux ratio, and Doppler shifted relative to each other due to their orbital motion. One technique to recover the spectra of the companion is secondary reconstruction through a differential spectrum~\citep{ferluga_separating_1997}. Spectra from different phases are shifted to the rest frame of the host star and subtracted to mutually cancel out the spectrum of the host star allowing the faint companion spectra to become visible. Advances in high-resolution and near-infrared (nIR) capabilities should enable this technique to be applied to BDs and planet companions, in which smaller RV shifts can be resolved and the contrast ratio of the smaller companion is improved.

Observing in the nIR is specifically desirable for the cooler sub-stellar and giant planet companions as their thermal emission is stronger in the infrared compared to the optical. This improves the contrast ratio between the host star and companion, providing favourable conditions for their detection and spectral separation. CRIRES, a high resolution nIR spectrograph, has made many prominent advances in recent years with the detection of atmospheric constituents, such as \(\textrm{CO}\) and \(\textrm{H}_{2}\textrm{O}\), atmospheric winds and thermal profiles, rotation and orbital motion, for both transiting and non-transiting planets~\citep[e.g.][]{snellen_orbital_2010, snellen_fast_2014, brogi_signature_2012, brogi_carbon_2014, brogi_rotation_2016, rodler_weighing_2012, dekok_detection_2013, piskorz_evidence_2016,  birkby_discovery_2017}.

The higher temperature and relatively larger size of BDs compared to giant-planets makes the development of spectral recovery techniques for BD companions a logical step towards the spectroscopic detection of planetary atmospheres. There has been the recent installation and continued development of many new high-resolution nIR spectrographs, such as, {CARMENES}~\citep{quirrenbach_carmenes_2014}, NIRPS~\citep{bouchy_nearinfrared_2017} or SPIRou~\citep{artigau_spirou_2014}, as well as, the CRIRES+~\citep{dorn_crires_2016} upgrade. These new instruments motivate the study of nIR-oriented methodologies for spectral recovery, and are of high importance due to the larger planet-to-star flux ratio provided by near-IR compared to the visible.

{The search and detection of faint secondary spectra is not only relevant to planetary atmospheres. \citet{kolbl_detection_2015} developed a method to detect the presence of optical secondary spectra down to a flux ratio of 1 per cent in the hosts of \emph{Kepler} transit candidates. The presence of which can cause ambiguities in the system configuration, and increase the uncertainty of the measured planet radius. The characterization of the false positive probability rate for Kepler has been found to be as high as \(\sim\)35 per cent~\citet{santerne_sophie_2012}.}

In this paper we apply two different techniques on FGK stars with BD companions with the aim to spectroscopically detect their companions. In Sect.~\ref{sec:data} we present the observations and reduction process as well as the spectral models used in this work. In Sect.~\ref{sec:spec_diff} we explain the differential spectral technique and its applicability to these observations while in Sect.~\ref{sec:results} we apply companion recovery using a \(\chi^{2}\) approach. In Sect.~\ref{sec:discussion} we discuss our results and in Sect.~\ref{sec:conclusions} we present our conclusions.

\section{Motivation and target selection}
\label{sec:motivation}
The work of~\citet{sahlmann_search_2011} identified several candidate brown dwarf companions of FGK stars with \(\rm M_2 \sin{i}\) values >\(\rm 10~M_{Jup}\). Seven candidates {from~\citet{sahlmann_search_2011}, which were visible in Period 89, were selected for further} observation using high resolution nIR spectroscopy in order to identify their stellar nature. The \textit{K}-band was used to achieve a high contrast relative to the host star, {\bl based on the} extreme V-K colour indexes (>7.8) {\bl of the companions}. The target host stars are presented in Table~\ref{tab:starparams} with their stellar parameters, while the companion orbital parameters are provided in Table~\ref{tab:orbitparams}.

We note that some of these orbital parameters have been refined in the literature since observations took place. For example three candidates have had their masses refined in recent works. The companion to {HD 211847} was determined to be a low mass star with an \(\rm M_2=155~M_{Jup}\)~\citep{moutou_eccentricity_2017}, while the companion to {HD 4747} was found to have a mass of \(\rm M_2=60~M_{Jup}\)~\citep{crepp_trends_2016}. The two companions of {HD 202206} (B and c) were found to have masses of \(\rm M_B =93.6~M_{Jup}\) and \(\rm M_c = 17.9~M_{Jup}\), respectively, classifying {HD 202206}c as a ``circumbinary brown dwarf''~\citep{benedict_hd_2017}. These targets with recently refined masses create good benchmarks for us to compare any results of the techniques developed in this paper, and show that these masses do span the BD -- low mass star range. All target companions except {HD 162020} (P=8.4 days) are in (very) long period orbits (P=0.7--38 years) with masses (or \(M\sin{i}\)) greater than \(\rm 10~M_{Jup}\).

\textit{K}-band spectra were obtained with the initial goal to achieve a direct detection of the companion spectra through the application of a spectral-differential approach~\citep[e.g.][]{ferluga_separating_1997, kostogryz_spectral_2013}. Doing so would have enabled a further constraint to be placed on their masses.  However the differential separation of the observations, the long orbital periods and, the small spectral shifts of the companions' lines resulted in an insufficient line separations to use a spectral-differential approach. This paper instead attempts to detect the companion spectra via fitting of these blended nIR spectra.

@@

The observations were performed in service mode during period 89 with run ID.~089.C-0977(A) between April and \textbf{September} 2012. An observation is composed of 8 individual spectra each with an integration time of 180 seconds, observed in a ABBAABBA nod cycle pattern to obtain a high (>180) signal-to-noise when combined.

@@

and \(A\), \(\mu\), \(\sigma\) are the amplitude, central wavelength, and standard deviation for each line respectively. {Although telluric lines are actually Voigt profiles, they are not fully resolved in the nIR and their shape is dominated by the instrumental profile. The instrumental profile for CRIRES has been shown to be well represented by a Gaussian shape~\citep{seifahrt_synthesising_2010}.}

The observed spectra contain two different components: the stellar and telluric lines multiplied together. These were fitted with two Gaussian-sum models multiplied together, with the identification of telluric and stellar lines performed {by hand} for each spectra, using the synthetic telluric models as the reference.
\begin{align}
I_{obs}(x) &= I_{tell}(x) \times {\bl I_{star}}(x) \nonumber \\
I_{obs}(x) &= \Big(1 - {\Sigma}_{j}\ G(x, A_{j}, {\mu}_{j}, {\sigma}_{j})\Big) \times \Big(1 - {\Sigma}_{k} G(x, A_{k}, {\mu}_{k}, {\sigma}_{k})\Big), \label{eqn:obs}
\end{align}

@@

The wavelength solution was obtained by fitting a second order polynomial, shown to be sufficient for higher precision RV studies~\citep[e.g.][]{bean_groundbased_2010, figueira_radial_2010, seifahrt_synthesising_2010}, to the centroid values \(\{\mu(x), \mu(\lambda)\}\) obtained from the telluric component of the observed spectra and telluric model respectively.

Much like issues with Th-Ar calibrations this method only works well when there is sufficient coverage of telluric lines on the detector. For the wavelength setting of these observations, the spectra from the second detector (top right panel of Fig.~\ref{fig:detector4allspectra}) only has two large telluric lines present with several small lines, with relative depths smaller than 1 per cent, which are difficult to identify. This deteriorated the calibration stability for the second detector. With the lack of telluric contamination and stellar lines on the second detector it may have been ideal for the detection of a faint secondary spectra; unfortunately the wavelength calibration quality varies in an inverse way.

We note that there are many variations on this wavelength-calibration technique including those integrated within programs such as \textsc{TelFit}~\citet{gullikson_correcting_2014}, and ESOs \textsc{Molecfit}~\citet{smette_molecfit_2015}, that perform telluric correction and re-calibrate the wavelength axis themselves. {Including features such as concurrent fitting of a stellar spectral model, adjusted for RV, along with the telluric model could help to improve the wavelength calibration preformed here. For example~\citet{piskorz_evidence_2016} performed wavelength calibration using only a telluric line model at other nIR wavelengths but had to specifically include a stellar model around 2\,$\mu$m where the telluric lines are weaker.}

@@

\subsubsection{Telluric correction}
\label{subsec:telluric_correction}
Ground based observations require the removal of the absorption lines introduced by Earth's atmosphere. The observations analysed here were taken in an atmospheric window of the \textit{K}-band in order to reduce the absorption introduced by the atmosphere~\citep{barnes_hd_2008}. To correct for the remaining telluric line contamination the spectra were divided by the TAPAS\citep{bertaux_tapas_2014} atmospheric transmission models for each observation. These synthetic telluric models were used to avoid the observing overhead necessary to perform telluric standard star exposures~\citep{vacca_method_2003}, and they have been demonstrated to be superior in the quality of the correction relative to the telluric standard approach~\citep[e.g.][]{cotton_atmospheric_2014}.

Before the correction, the depth of the telluric lines were re-scaled to match the airmass of the observation using the relation \(\rm T = T^{\beta}\), where \(\rm T\) is the telluric spectrum and \(\beta\) is the airmass ratio between the observation and model. This changed the depth of most absorption lines to match the observations, but does not correctly scale the deeper \(\rm H_{2}O\) lines. The scaled telluric model is interpolated to the wavelengths of the observed spectrum and then used to correct the observed spectra through division, leaving behind a telluric corrected spectra. An example of a telluric corrected spectra is shown in the middle panel of Fig.~\ref{fig:spectral_example}, with the light blue shading indicating where the deeper telluric lines were.

>>>>

    % Abstract of the paper
    \begin{abstract}
        {\bl In this paper we attempt to detect the near-infrared (nIR) spectrum of candidate brown dwarf (BD) companions around FGK stars in order to assert or discard their stellar nature. First, Individual nIR spectra are fitted to a synthetic binary model comprised of two PHOENIX-ACES spectra using a $\chi^2$ approach. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models. This procedure was unable to successfully detect the spectra of the most massive companion in the sample. We explore how the companion recovery fitting performs on simulated observations and discuss reasons for the non-detection observed. From the injection-recovery analysis, this technique, in its current form, is insufficient to recover a companion below 3800~K, corresponds to an upper mass limit of around \(\rm 600~M_{Jup}\). A strong discrepancy between models and observations was found and is put forward as the main reason for the non-detection. This work highlights the challenges in the spectral detection of faint companions, and in particular the limitations of the companion detection with synthetic models at low companion/host flux ratios.}

@@

    \section{Introduction}
    \label{sec:intro}
    Brown dwarfs (BDs) are sub-stellar objects unable to achieve hydrogen fusion; with masses around \(13-80~\textrm{M}_{Jup}\)~\citep{chabrier_theory_2000} these objects bridge the gap between low-mass stars and giant planets. Without sustained fusion, brown-dwarfs cool down over time with an age-dependent cooling rate. Therefore, there is an inherent degeneracy between the mass, age and luminosity of a given BD\citep{burrows_nongray_1997}. {\bl The direct measurement of the mass of brown dwarf is the first step to break this degeneracy.}

    {\bl By observing BD in both radial velocity (RV) and astrometry, one can determine the objects' true masses}. The RV technique provides a mass lower-limit (\(\textrm{M}_{2}\sin{i}\)) of binary and planetary companions, while the complementary astrometry measurements can often provide mass upper-limits~\citep[e.g.][]{sahlmann_search_2011}. {\bl by observing with the two techniques simultaneously one can obtain a tridimensional characterization of the orbit.}

    {\bl Unfortunately, when compared to stellar or planetary companions, BD companions in short period orbits are very rare around Sun-like stars. Characterizing the few stars of this \emph{brown dwarf desert}~\citep{halbwachs_exploring_2000,zucker_analysis_2001,sahlmann_search_2011} and the establishment of benchmark BDs ~\citep[e.g.][]{crepp_trends_2016} is crucial to constrain formation and evolution theories~\citep{whitworth_formation_2007} and in understanding this sub-stellar population.}

    Recently, there has been a renewed interest in BD candidates triggered by exoplanetary searches. {\bl While several works found similar properties on the BD and exoplanet populations, like a similar {\bl mass} density~\citep{hatzes_definition_2015}, others found intriguing differences, like the different host metallicity ~\citep{santos_observational_2017, schlaufman_evidence_2018}, a strong hint of different formation mechanisms.}

    Measuring or tightening the constraints of BD masses improves the understanding of mass dependence on BD formation processes. For instance, there is growing evidence that the larger giant planets and BD companions do not follow the well known metallicity-giant planet correlation seen in main-sequence stars with planets~\citep[e.g.][]{santos_spectroscopic_2004,santos_observational_2017, maldonado_searching_2017}. Photometry along with stellar evolution models~\citep[e.g.][]{baraffe_evolutionary_2003,allard_btsettl_2013} can also be used to estimate the mass of BD companions~\citep[e.g.][]{moutou_eccentricity_2017} if there is sufficient orbital separation, and a precise determination of the age~\citep[e.g.][]{soderblom_ages_2010}.

    {\bl At the level of direct spectral analysis, one can attempt to recover the spectra of the BD companion through a differential analysis~\citep{ferluga_separating_1997}. Spectra collected at different orbitalphases are shifted to the rest frame of the host star and mutually subtracted to cancel out the spectrum of the host star, allowing the faint companion spectra to surface.} Advances in high-resolution and near-infrared (nIR) capabilities should enable this technique to be applied to BDs and planet companions, in which smaller RV shifts can be resolved and the contrast ratio of the smaller companion is improved.

    Observing in the nIR is specifically desirable for the cooler sub-stellar and giant planet companions as their thermal emission is stronger in the infrared {\bl when compared to the optical, improving the contrast ratio between the host star and companion. The high-resolution nIR spectrograph CRIRES, has allowed significant advances in recent years with the detection of atmospheric signatures like \(\textrm{CO}\) and \(\textrm{H}_{2}\textrm{O}\), atmospheric winds and thermal profiles, rotation and orbital motion, for both transiting and non-transiting planets~\citep[e.g.][]{snellen_orbital_2010, snellen_fast_2014, brogi_signature_2012, brogi_carbon_2014, brogi_rotation_2016, rodler_weighing_2012, dekok_detection_2013, piskorz_evidence_2016,  birkby_discovery_2017}.}

    The higher temperature and relatively larger size of BDs when compared to giant-planets makes the development of spectral recovery techniques for BD companions a logical step capable of providing input to formation models. {\bl The recent advent of many new high-resolution nIR spectrographs, such as, {CARMENES}~\citep{quirrenbach_carmenes_2014}, NIRPS~\citep{bouchy_nearinfrared_2017} or SPIRou~\citep{artigau_spirou_2014}, as well as, the CRIRES+~\citep{dorn_crires_2016} upgrade, motivate the study of nIR-oriented methodologies for spectral recovery.}

    {\bl It is important to note that the search and detection of faint secondary spectra is not only relevant to planetary atmospheres, and has been attempted previously for the stellar and subtellar regime.} \citet{kolbl_detection_2015} developed a method to detect the presence of optical secondary spectra down to a flux ratio of 1 per cent in the hosts of \emph{Kepler} transit candidates. The presence of which can cause ambiguities in the system configuration, {\bl and introduce important systematics of the measured planet radius.} The characterization of the false positive probability rate for Kepler has been found to be as high as \(\sim\)35 per cent~\citet{santerne_sophie_2012},{\bl highlighting the strong incidence of the problem.}

    {\bl In this paper we aim at detecting spectrcoscopically the BD companions of FGK stars. In Sect.~\ref{sec:motivation} we present the motivation for target selection, and in Sect.~\ref{sec:data} we present the observations and reduction process, along with the spectral models used in this work. In Sect.~\ref{sec:companion_recovery} we explain our companion recovery technique and its applicability to these observations,} while in Sect.~\ref{sec:results} we apply companion recovery using a \(\chi^{2}\) approach. In Sect.~\ref{sec:discussion} we discuss our results and in Sect.~\ref{sec:conclusions} we present our conclusions.

    \section{Motivation and target selection}
    \label{sec:motivation}
    \citet{sahlmann_search_2011} identified several candidate brown dwarf companions of FGK stars with \(\rm M_2 \sin{i}\) values >\(\rm 10~M_{Jup}\).{\bl, These objects were among the best characterized BD at the time of the observations, and we selected seven candidates visible in Period 89. The \textit{K}-band was selected to achieve a high contrast of the BD relative to the host star,  based on the extreme V-K colour indexes (>7.8) of the companions}.

    The target host stars are presented in Table~\ref{tab:starparams} along with their stellar parameters, while the companion orbital parameters are provided in Table~\ref{tab:orbitparams}.

    We note that some of these orbital parameters have been refined in the literature since the observations took place. The companion to {HD 211847} was found to be a low mass star with an \(\rm M_2=155~M_{Jup}\)~\citep{moutou_eccentricity_2017}, while the companion to {HD 4747} was found to have a mass of \(\rm M_2=60~M_{Jup}\)~\citep{crepp_trends_2016}. The two companions of {HD 202206} (B and c) were found to have masses of \(\rm M_B =93.6~M_{Jup}\) and \(\rm M_c = 17.9~M_{Jup}\), respectively, classifying {HD 202206}c as a ``circumbinary brown dwarf''~\citep{benedict_hd_2017}. These targets with recently refined masses create good benchmarks for us to compare any results of the techniques developed in this paper, and show that these masses do span the BD -- low mass star range. All target companions except {HD 162020} (P=8.4 days) are in (very) long period orbits (P=0.7--38 years) with masses (or \(M\sin{i}\)) greater than \(\rm 10~M_{Jup}\).

    {\bl \textit{K}-band spectra were obtained with the initial goal to achieve a direct detection of the companion spectra through the application of a spectral-differential approach~\citep[e.g.][]{ferluga_separating_1997, kostogryz_spectral_2013}. Doing so would have enabled a further constraint to be placed on their masses.  However the short time elapsed between observations and the long orbital periods led to an insufficient line separations to use a spectral-differential approach. This paper instead attempts to detect the companion spectra via fitting of these blended nIR spectra.}

@@

    The observations were conducted in service mode during period 89 under run ID.~089.C-0977(A) between April and \textbf{September} 2012. An observation is composed of 8 individual spectra each with an integration time of 180 seconds, observed in a ABBAABBA nod cycle pattern to obtain a high (>180) signal-to-noise when combined.

@@

    and \(A\), \(\mu\), \(\sigma\) are the amplitude, central wavelength, and standard deviation for each line, respectively. {\bl Even though telluric lines are formally described by Voigt profiles, at 50 000 of resolution the lines are not fully resolved in the nIR and as such their shape is dominated by the convolution with the instrumental profile.\footnote{The instrumental profile for CRIRES has been shown to be well represented by a Gaussian shape~\citep{seifahrt_synthesising_2010}}.}

    The observed spectra contain thus two different components: the stellar and the telluric lines. {\bl Just like the telluric conmponets, the stellar spectra can be well approximated by a sum of Gaussian Functions. The observed spectra correspond to the product of the stellar and telluric components. The identification of telluric and stellar lines is done assuming the synthetic telluric models are complete and allow to identify all the telluric lines. The spectra can then be represented mathematically by} 
    \begin{align}
    I_{obs}(x) &= I_{tell}(x) \times {\bl I_{star}}(x) \nonumber \\
    I_{obs}(x) &= \Big(1 - {\Sigma}_{j}\ G(x, A_{j}, {\mu}_{j}, {\sigma}_{j})\Big) \times \Big(1 - {\Sigma}_{k} G(x, A_{k}, {\mu}_{k}, {\sigma}_{k})\Big), \label{eqn:obs}
    \end{align}

@@

    The wavelength solution was obtained by fitting a second order polynomial, shown to be sufficient for higher precision RV studies~\citep[e.g.][]{bean_groundbased_2010, figueira_radial_2010, seifahrt_synthesising_2010}, to the centroid values \(\{\mu(x), \mu(\lambda)\}\) obtained from the telluric component of the observed spectra and telluric model, respectively.

    {\bl Just like for the Th-Ar calibrations, this method only works when the available telluric lines cover the detector.} For the wavelength setting of these observations, the spectra from the second detector (top right panel of Fig.~\ref{fig:detector4allspectra}) only have two large telluric lines present with several small lines, with relative depths smaller than 1 per cent, which are difficult to identify. This deteriorated the calibration stability for the second detector. {\bl While the lack of telluric contamination and stellar lines on the second detector makes it ideal for the detection of a faint secondary spectra it makes the process of wavelength calibration much more difficult.}

    We note that there are many variations on this wavelength-calibration technique, including those integrated within programs such as \textsc{TelFit}~\citet{gullikson_correcting_2014}, and ESOs \textsc{Molecfit}~\citet{smette_molecfit_2015}, that perform telluric correction and re-calibrate the wavelength axis themselves. {\bl Including features such as concurrent fitting of a stellar spectral model, adjusted for RV, along with the telluric model, could help to improve the wavelength calibration performed here. For example~\citet{piskorz_evidence_2016} while performing wavelength calibration using only a telluric line model on a wide range of wavelength, had to specifically include a stellar model around 2\,$\mu$m where the telluric lines are weaker.}

@@

    \subsubsection{Telluric correction}
    \label{subsec:telluric_correction}
    Ground based nIR observations require the removal of the absorption lines introduced by Earth's atmosphere. The observations analysed here were taken in an atmospheric window in the \textit{K}-band in order to reduce the absorption introduced by the atmosphere~\citep{barnes_hd_2008}. To correct for the remaining telluric line contamination, the spectra were divided by the TAPAS\citep{bertaux_tapas_2014} atmospheric transmission models computed for each observation. These synthetic telluric models were used to avoid the observing overhead necessary to perform telluric standard star exposures~\citep{vacca_method_2003}, and they have been demonstrated to be superior in the quality of the correction relative to the telluric standard approach~\citep[e.g.][]{cotton_atmospheric_2014}.
